---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# groupie

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/groupie)](https://cran.r-project.org/package=groupie)
[![Travis build status](https://travis-ci.org/nacnudus/groupie.svg?branch=master)](https://travis-ci.org/nacnudus/groupie)
[![Codecov test coverage](https://codecov.io/gh/nacnudus/groupie/branch/master/graph/badge.svg)](https://codecov.io/gh/nacnudus/groupie?branch=master)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/nacnudus/groupie?branch=master&svg=true)](https://ci.appveyor.com/project/nacnudus/groupie)
<!-- badges: end -->

The groupie package provides `groups_split()` to create copies of a data frame
with different combinations of grouping variables.  This is useful for
summarising data several ways in one go.

## Installation

You can install the development version of groupie from github with

``` r
# install.packages("remotes") # if not already installed
remotes::install_github("nacnudus/groupie")
```

## Example

```{r library}
library(groupie)

library(dplyr)
library(purrr)
```

Summarise by

* `cyl`
* `cyl` and `am`
* `cyl`, `am` and `mpg`

```{r hierarchy}
mtcars %>%
  group_by(cyl, am, gear) %>%
  groups_split(hierarchy) %>%
  map(summarise, mpg = mean(mpg))
```

Summarise by each one of `cyl`, `am` and `mpg`.

```{r k_combinations_1}
mtcars %>%
  group_by(cyl, am, gear) %>%
  groups_split(k_combinations, 1L) %>%
  map(summarise, mpg = mean(mpg))
```

Summarise by all pairs of `cyl`, `am` and `mpg`.

```{r k_combinations_2}
mtcars %>%
  group_by(cyl, am, gear) %>%
  groups_split(k_combinations, 2L) %>%
  map(summarise, mpg = mean(mpg))
```

## Contribute

Please note that the 'groupie' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
